Analysis-ready VCF at Biobank scale using Zarr

### 2024-05-30 paper.tex
Fix caption
Various figure tidy-ups

\begin{figure}
\includegraphics{figures/whole-matrix-decode}
\caption{Genotype decoding performance.
Total CPU time required to decode genotypes into memory using the zarr-python
and Savvy C++ APIs for the data in Figure~\ref{fig-data-storage}.
This corresponds to maximum rate of 1.2GiB/s for Zarr and 5.7GiB/s
for Savvy. [TODO add data for 1 million samples]
\label{fig-whole-matrix-decode}}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figures/whole-matrix-decode}
\caption{Genotype decoding performance.
Total CPU time required to decode genotypes into memory using the Zarr-Python
and Savvy C++ APIs for the data in Figure~\ref{fig-data-storage}.
This corresponds to a maximum rate of 1.2GiB/s for Zarr (Zstd + BitShuffle),
3.9 GiB/s Zarr (Zstd), and 6.6 GiB/s for Savvy. 
\label{fig-whole-matrix-decode}}
\end{figure}
